---
title: "Project 3 : Supermarket sale"
output: html_notebook
---

---
author: "TUAN LINH DAO"
date: "8/16/2021"
---

####
# Project 3 : Supermarket sale
####
# A. Branch A :
####
### Load package:
####
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(RColorBrewer)
```

####
# I/ Explore data :
####
# 1) Import dataset :
####
```{r}
data <- read.csv(file.choose(), header = T)
data
```
####
# 2) Summarize data :
####
## a.1) Summary table : 
####
```{r}
summary(data)
```
####
## a.2) Dimension of dataset :
####
```{r}
dim(data)
```

####
## b) Unique value :
####
### b.1) Using "unique" function :
####
```{r}
# Branch :
a <- unique(data$Branch)
a
# City :
b <- unique(data$City)
b
# Customer type :
c <- unique(data$Customer.type)
c
# Gender :
d <- unique(data$Gender)
d
# Product line :
e <- unique(data$Product.line)
e
# Payment :
f <- unique(data$Payment)
f
```
####
### b.2) Using "distinct" function with %>% operator :
####
```{r}
# Branch :
a_1 <- data %>%
  distinct(data$Branch)
a_1
# City :
b_1 <- data %>%
  distinct(data$Customer.type)
b_1
# Customer type :
c_1 <- data %>%
  distinct(data$Customer.type)
c_1
# Gender :
d_1 <- data %>%
  distinct(data$Gender)
d_1
# Product line :
e_1 <- data %>%
  distinct(data$Product.line)
e_1
# Payment :
f_1 <- data %>%
  distinct(data$Payment)
f_1
```
####
# II/ Member table and non-member with product line:
####
# 3) Member table and non-member table of branch A:
####
## Sort data for branch A uniquely :
####
```{r}
m_table <- data[data$Branch == "A", ]
m_table
```
####
## a) Count the quantity for each product line based on customer type, gender :
####
```{r}
m <- m_table %>%
  count(m_table$Customer.type,m_table$Gender,m_table$Product.line)
m
```
####
## b) Table for member of branch A:
####
### *) Member table :
####
```{r}
m1 <- m[m$`m_table$Customer.type` == "Member", ]
m1
# Rename all columns of member table :
colnames(m1) <- c("Customer type","Gender","Product_line","Quantity")
colnames(m1)
View(m1)
```
####
### *) Barplot using ggplot package:
####
```{r}
m <- ggplot(m1,aes(x=Gender,y=Quantity,fill=Product_line)) +
  geom_bar(stat='identity',position = 'dodge') +
  labs(title = "Product line by gender (for member)",
       y="Quantity",
       x="Gender") +
  geom_text(m1,mapping = aes(label=Quantity),stat = 'identity',position_dodge(width = 1)) #+
  #theme(legend.title = element_blank()) + 
  #theme_fivethirtyeight()
m
```
####
## c) Table for non-member of branch A:
####
### *) Non-member table :
####
```{r}
n_table <- m[m$`m_table$Customer.type`=="Normal", ]
n_table
colnames(n_table) <- c("Customer type","Gender","Product_line","Quantity")
colnames(n_table)
View(n_table)
```
####
### *) Barplot using ggplot package :
####
```{r}
n <- ggplot(n_table,aes(x=Gender,y=Quantity,fill=Product_line)) +
  geom_bar(stat='identity',position = 'dodge') +
  labs(title = "Product line by gender (for non-member)",
       y="Quantity",
       x="Gender") +
  geom_text(n_table,mapping = aes(label=Quantity),stat = 'identity',position_dodge(width = 1)) #+
  #theme(legend.title = element_blank()) + 
  #theme_fivethirtyeight()
n
```
####
### *) Combining 2 chart:
####
```{r}
figure <- ggarrange(m, n,
                    labels = c("Member", "Non-member(normal)"),
                    ncol = 1, nrow = 2, hjust = 4)
figure
```
####
# III/ Member table and non-member with rating(shopping experience on scale from 1 to 10):
####
## *) Create a dataframe :
####
```{r}
data1 <- data.frame(data$Customer.type,data$Gender,data$Rating,data$gross.income)
data1
```
####
### a) "Member" :
####
### *) Table :
####
```{r}
m_table1 <- data1[data1$data.Customer.type == "Member", ]
m_table1
colnames(m_table1) <- c("Customer type","Gender","Rating","Gross_income")
colnames(m_table1)
```
####
### *) Boxplot using ggplot :
####
```{r}
m_1 <- ggplot(m_table1,aes(x=Gender,y=Rating,fill=Gender)) +
  geom_boxplot() +
  labs(title = "Rating by gender (for member)",
       y="Rating",
       x="Gender") + 
  stat_summary(fun = mean, geom = "point", shape=16, size=3, color="white") +
  scale_fill_manual(values=c("mediumvioletred", "mediumspringgreen")) 
m_1
```
####
### b) "Member" :
####
### *) Table :
####
```{r}
n_table1 <- data1[data1$data.Customer.type == "Normal", ]
n_table1
colnames(n_table1) <- c("Customer type","Gender","Rating","Gross_income")
colnames(n_table1)
```
####
### *) Boxplot using ggplot :
####
```{r}
n_1 <- ggplot(n_table1,aes(x=Gender,y=Rating,fill=Gender)) +
  geom_boxplot() +
  labs(title = "Rating by gender (for member)",
       y="Rating",
       x="Gender") + 
  stat_summary(fun = mean, geom = "point", shape=16, size=3, color="white") +
  scale_fill_manual(values=c("mediumvioletred", "mediumspringgreen")) 
n_1
```
####
### c) Combining 4 boxplots :
####
```{r}
figure1 <- ggarrange(m_1, n_1,
                    labels = c("Member", "Non-member(normal)"),
                    ncol = 2, nrow = 1, hjust = 4)
figure1
```
####
### Comment: Both "member" or "non-member" have quite good shopping experience (almost 50% people in both genders, both types of customer have ranked their stratification 7/10). 
####
# IV/ Gross income:
####
## a) Boxplot for "Member":
####
```{r}
m_2 <- ggplot(m_table1,aes(x=Gender,y=Gross_income,fill=Gender)) +
  geom_boxplot() +
  labs(title = "Member",
       y="Gross income",
       x="Gender") + 
  stat_summary(fun = mean, geom = "point", shape=16, size=3, color="white") +
  theme(plot.title = element_text(size = 20, color = "midnightblue")) +
  #stat_boxplot(geom = "errorbar", width=0.3) +
  scale_fill_manual(values=c("violetred1", "mediumturquoise")) 
m_2
```
####
## b) Boxplot for "Non-member":
####
```{r}
n_2 <- ggplot(n_table1,aes(x=Gender,y=Gross_income,fill=Gender)) +
  geom_boxplot(outlier.colour = "blue",outlier.shape = 16) +
  labs(title = "Non-member",
       y="Gross income",
       x="Gender") + 
  stat_summary(fun = mean, geom = "point", shape=16, size=3,color="white") +
  theme(plot.title = element_text(size = 20, color = "midnightblue")) +
  #stat_boxplot(geom = "errorbar", width=0.3) +
  scale_fill_manual(values=c("violetred1", "mediumturquoise")) 
n_2
```
####
## c) Combining 4 boxplots:
####
```{r}
figure2 <- ggarrange(m_2,n_2,
                     labels = c("Member", "Non-member(normal)"),
                    ncol = 2, nrow = 1, hjust = 4)
figure2
```
####
### Comment:
####
### *) "Member":
#### 50% of female and 50% male have the the same median in gross income(about 12), female's 3rd quartile value is greater than male's 3rd quartile value(almost 25 > 22). Both genders also have the same 1st quartile value(slightly more than 5).For female, the max value even reaches to 50, for male it's just 45.There are no outlier here.
####
### *) "Non-member":
#### Female has greater median value than male(14 > 10),it seems like there isn't much difference in 3rd quartile value for both genders.Both genders have the same max value.Notice that there is even some outliers in this chart for "non-member", male just has one more outlier than female(almost reach to 50).
####
# V/Payment:
####
## *) Dataframe :
####
```{r}
data2 <- data.frame(data$Branch,data$Customer.type,data$Gender,data$Payment)
data2
```
####
## *) Sort data for branch A uniquely:
####
```{r}
p_table <- data2[data2$data.Branch=="A", ]
p_table
```
####
## *) The amount of people in each type of payment based on customer type and gender:
####
```{r}
p <- p_table %>%
  count(p_table$data.Customer.type,p_table$data.Gender,p_table$data.Payment) %>%
  mutate(prop_payment = round((n/sum(n))*100,2))
p
sum(p$n)
#View(p)
```
####
## *) Payment table for "Member":
####
```{r}
p_m <- p[p$`p_table$data.Customer.type`=="Member", ]
p_m
colnames(p_m) <- c("Customer_type","Gender","Payment","Quantity","%")
colnames(p_m)
```
####
## *) Payment table for "Non-member":
####
```{r}
p_n <- p[p$`p_table$data.Customer.type`=="Normal", ]
p_n
colnames(p_n) <- c("Customer_type","Gender","Payment","Quantity","%")
colnames(p_n)
```
####
## *) ggplot chart:
####
### "Payment by Member":
####
```{r}
p1 <- ggplot(p_m,aes(x=Gender,y=Quantity,fill=Payment)) +
  geom_bar(stat='identity',position = 'dodge') +
  labs(title = ("Payment by Member"),
       y="Quantity",
       x="Gender") +
  geom_text(p_m,mapping = aes(label=Quantity),stat = 'identity',position_dodge(width = 1))
p1
```
####
### "Payment by Non-member":
####
```{r}
p2 <- ggplot(p_n,aes(x=Gender,y=Quantity,fill=Payment)) +
  geom_bar(stat='identity',position = 'dodge') +
  labs(title = ("Payment by Non-member"),
       y="Quantity",
       x="Gender") +
  geom_text(p_n,mapping = aes(label=Quantity),stat = 'identity',position_dodge(width = 1))
p2
```
####
### Combining chart:
####
### a) Bar chart:
####
```{r}
figure3 <- ggarrange(p1,p2,
                     labels = c("Member","Non-member"),
                     ncol=1,nrow = 2,hjust = 4)
figure3
```

####
### b) Pie chart(for whole branch A):
####
### *) Dataframe:
####
```{r}
P_table <- p_table %>%
  count(p_table$data.Branch,p_table$data.Payment) %>%
  mutate(Percentage = (n/sum(n))*100)
P_table
colnames(P_table) <- c("Branch","Payment","Quantity","Percentage")
colnames(P_table)
```
####
### *) Pie chart using ggpie from ggpubr package:
####
```{r}
labs <- paste0(p_n1$Payment, " (", round(P_table$Percentage,2), "%)")
labs
# Female member :
ppg_A <- ggpie(Py_nfm,"Prop_pay",label = labs,
   lab.pos = "in", lab.font = "white",
      fill = "Payment", 
      color = "white",
       palette = c("#00AFBB", "#E7B800", "#FC4E07")) +
  ggtitle("Proportion for each type of payment in branch A") +
  theme(plot.title = element_text(hjust = 0.5,size = 20))
ppg_A
```

